DraftOne

### 2016-06-25 writing/JSSDraft/JSSDraft.Rmd
Work on JSS draft

@@

* False positive rate / type I error rate (percent of time significant effect is detected-- i.e., null hypothesis is rejected-- when there is not a true effect) \citep{Bellan2015, Johnson2015}
* Power / Statistical power to detect a true effect of a certain size / empirical power (percent of simulations in which a true effect of a certain size is identified with a p-value of 0.05 or lower; i.e., probability of rejecting the null hypothesis when the null hypothesis is false) \citep{Bellan2015, Johnson2015, Gaye2015, Green2016, Beaujean2014}
* Precision of effect estimate (average confidence interval width over all simulations; some studies give average half-width) \citep{Johnson2015, Beaujean2014}
* Coverage / 95% confidence inverval coverage (percent of 95% confidence intervals from simulations that include the true effect size) \citep{Johnson2015, Beaujean2014}
* Bias in effect estimate \citep{Johnson2015}
* Margin of error [?] \citep{Johnson2015}
* Sample size required to detect a certain effect size \citep{Burton2009, Gaye2015, Green2016, Beaujean2014}
* Time to achieve required number of cases \citep{Burton2009}
* Power curve \citep{Beaujean2014}
* Accuracy curve \citep{Beaujean2014}

>>>>

\citet{Schoemann2014} demonstrate how to use simulation studies to assess power for study designs with planned missing data.

@@

* False positive rate / type I error rate (percent of time significant effect is detected-- i.e., null hypothesis is rejected-- when there is not a true effect) \citep{Bellan2015, Johnson2015}
* Power / Statistical power to detect a true effect of a certain size / empirical power (percent of simulations in which a true effect of a certain size is identified with a p-value of 0.05 or lower; i.e., probability of rejecting the null hypothesis when the null hypothesis is false) \citep{Bellan2015, Johnson2015, Gaye2015, Green2016, Beaujean2014}
* Precision of effect estimate (average confidence interval width over all simulations; some studies give average half-width) \citep{Johnson2015, Beaujean2014}
* Coverage / 95% confidence inverval coverage (percent of 95% confidence intervals from simulations that include the true effect size) \citep{Johnson2015, Beaujean2014}
* Bias in effect estimate / relative parameter estimate bias / relative bias in point estimate \citep{Johnson2015, Beaujean2014, Schoemann2014}
* Relative standard error bias / standard error bias \citep{Beaujean2014, Schoemann2014}
* Margin of error [?] \citep{Johnson2015}
* Sample size required to detect a certain effect size \citep{Burton2009, Gaye2015, Green2016, Beaujean2014, Schoemann2014}
* Time to achieve required number of cases \citep{Burton2009}
* Power curve \citep{Beaujean2014}
* Accuracy curve \citep{Beaujean2014}
